### 2013-07-23 Tex/chapters/results.tex
Kleinigkeiten vervollständigt

    there can never be to much cross and consistency checks, the ratio

@@

@@

@@

                \subref{sfig:susCrossCheck:RNG} the RNG and
                \subref{sfig:susCrossCheck:GG} the GG.

>>>>

    there can never be to much cross- and consistency checks, the ratio

@@

        \subfigure[for a RNG][]

@@

        \subfigure[for a GG][]

@@

                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
